---
title: "Project plotting"
output: html_document
---

```{r}
gas_stations <- read.csv("gas_stations.csv")
park <- read.csv("park.csv")
cafe <- read.csv("cafe.csv")
convenience_store <- read.csv("convenience_stores.csv")
shopping_mall <- read.csv("shopping_mall.csv")
```

```{r}
# enable google API key
library(ggmap)
register_google(key='AIzaSyAFwIr0aBkkLxXzihnK_LPlh-Ph77FZy44')
```
# draw the route between 2 locations
```{r}
from <- "ESSO BUKIT TIMAH, singapore"
to <- "TreeTop Walk, singapore"

trek_df <- trek(from, to, mode="walking", alternatives = F)


qmap("ESSO BUKIT TIMAH, singapore", zoom = 13) +
  geom_path(
    aes(x = lon, y = lat), colour = "red", size = 0.5,
    data = trek_df, lineend = "round")
``` 

# calculate the distance between two locations
```{r}
from <- "ESSO BUKIT TIMAH, singapore"
to <- "Caltex Alexandra, singapore"

mapdist(from, to, mode = "bicycling")
```


```{r}
as.POSIXct("2014-10-27 18:00:00 PDT")

```


# calculate the distance between two locations
```{r}
## geographic coordinates are accepted as well

wh <- as.numeric(geocode("ESSO BUKIT TIMAH, singapore"))
lm <- as.numeric(geocode("Caltex Alexandra, singapore"))
mapdist(wh, lm, mode = "walking")
```

#Attempt using Mapsapi
```{r}
library(mapsapi)
library(xml2)
key='AIzaSyAFwIr0aBkkLxXzihnK_LPlh-Ph77FZy44'

#gas_stations$long_lat <- lapply(1:nrow(gas_stations), 
                               # function(i) #c(gas_stations$geometry.location.lng[i],
                                              #gas_stations$geometry.location.lat[i]))

esso_bt <- gas_stations[1, ] #1st row of gas_stations data
TreeTop <- park[2,] 
#shell <- gas_stations[2, ]#2nd row of gas_stations data
#esso_bt$geometry.location.lat 

doc <- mp_directions(
  origin = c(esso_bt$geometry.location.lng, esso_bt$geometry.location.lat),
  waypoints = c("Durian Loop", "Durian Loop", "Upper Peirce Reservoir"),
  destination = c(TreeTop$geometry.location.lng, TreeTop$geometry.location.lat),
  alternatives = FALSE,
  key = key,
  mode = "walking",
  quiet = TRUE
) 
#the output is a XML document with Google Maps Geocode API response - whatever that means

doc = as_xml_document(doc) #apparently we have to read it into an XML document - whatever that means
r <- mp_get_routes(doc) #mp_get_routes is a function to uhm..get the route

#distance <- mp_get_matrix(doc, value="distance_m")

library(leaflet)

leaflet() %>% addTiles() %>% addPolylines(data = r, opacity = 1, weight = 4) #can specify other things here tbh
```


```{r}
locations = c("Tel-Aviv", "Jerusalem", "Neve Shalom")
# Driving times 
doc = mp_matrix(
origins = locations,
destinations = locations,
mode = "driving",
departure_time = Sys.time() + as.difftime(10, units = "mins"), key = key
)

# Public transport times doc = mp_matrix(
mp_get_matrix(doc, value = "distance_m")
mp_get_matrix(doc, value= "distance_text")
mp_get_matrix(doc, value= "duration_s")
mp_get_matrix(doc, value= "duration_text")
mp_get_matrix(doc, value= "duration_in_traffic_s")
mp_get_matrix(doc, value= "duration_in_traffic_text")


```


# use s2
```{r}
library('s2')

nearest <- function(curr.long.lat, next.loc){ # curr.long.lat is a vector of the current location, next.loc is a character of the next target location e.g. "gas stations"
  # read csv of next.loc
  next_loc <- read.csv(gsub(" ", "", paste(gsub(" ", "_", next.loc), ".csv")))
  
  curr.long.latv <- s2_lnglat(curr.long.lat[1], curr.long.lat[2])
  target.loc.long.lat <- s2_lnglat(next_loc$geometry.location.lng, next_loc$geometry.location.lat)
  closest.long.lat <- s2_closest_feature(curr.long.latv, target.loc.long.lat)
  closest.coordinate <- c(next_loc[closest.long.lat, "geometry.location.lng"],next_loc[closest.long.lat, "geometry.location.lat"])

  return (closest.coordinate) # returns a vector of the long and lat of the closest next location, to be supplied to the mp_directions function
}


nearest.loc.mat <- function(origin, ...){
  locations <- list(...)
  
  if (is.null(locations)){
    return(0) # placeholder for when no locations are supplied as input arguments; to be replaced with function to generate random route that fulfills other restraints
    
  } else {
    output <- list()
    
    for (location in locations){
      next.long.lat <- nearest(origin, location)
      output <- append(output, next.long.lat)
      origin <- next.long.lat
    }
  }
  
  output <- matrix(unlist(output), ncol=length(locations), byrow=F)
  colnames(output) <- locations
  
  return (output)
}
```

```{r}
nearest.loc.mat(c(103.799000 , 1.330022), "cafe", "convenience stores", "shopping mall")
```


# pseudocode
1. user inputs his address/current location and the locations he/she wanna pass by in his/her run. we use map_geocode() to retrieve his/her current location's long and lat

2. pass this long lat and the next location e.g. "gas stations" to the function i sent to u to get the row number of the corresponding csv (in this case gas_stations.csv) with the place that is nearest to the input longlat

3. plot the route using mp_directions, then use mp_get_matrix() to get the distance of the route, add to a distance numeric variable created at the start of the function

4. repeat 2, 3 until all locations are satisfied.

5. for the last location we optimise a plot so that the distance is closest to the input total distance


# use geosphere to define a function to get nearest cafe
```{r}
library(geosphere)
library(dplyr)
cafe <- cafe[!is.na(cafe$geometry.location.lng) & !is.na(cafe$geometry.location.lat),]

nearest_cafe <- data.frame(Nearest=NA, Distance=NA, Lng=NA, Lat=NA)
  
origin.coords <- c(103.799000 , 1.330022)
cafe.coords <- cafe %>% select(geometry.location.lng, geometry.location.lat)
distances <- distm(origin.coords, cafe.coords, fun=distGeo)[1,]
diff <- abs(distances - 750)
row.num1 <- which.min(diff)

nearest_cafe[1,]$Nearest <- cafe$name[row.num1]
nearest_cafe[1,]$Distance <- distances[row.num1] %>% round(-1) %>% as.integer
nearest_cafe[1,]$Lng <- cafe$geometry.location.lng[row.num1]
nearest_cafe[1,]$Lat <- cafe$geometry.location.lat[row.num1]
  
print(nearest_cafe)
```

# get nearest convenience store from cafe
```{r}
library(geosphere)
library(dplyr)
convenience_store <- convenience_store[!is.na(convenience_store$geometry.location.lng) & !is.na(convenience_store$geometry.location.lat),]

nearest_convenience_store <- function(n){
  nearest_conve_store <- data.frame(Nearest=NA, Distance=NA, Lng=NA, Lat=NA)
  
  cafe.coords <- cafe[n,] %>% select(geometry.location.lng, geometry.location.lat)
  conve_store.coords <- convenience_store %>% select(geometry.location.lng, geometry.location.lat)
  #distances <- distm(cafe.coords, conve_store.coords, fun=distGeo)[1,]
  distances <- distm(origin.coords, conve_store.coords, fun=distGeo)[1,]
  diff <- abs(distances - 750)
  row.num <- which.min(diff)
  #row.num < which.min(distances)
  
  nearest_conve_store[1,]$Nearest <- convenience_store$name[row.num]
  nearest_conve_store[1,]$Distance <- distances[row.num] %>% round(-1) %>% as.integer
  nearest_conve_store[1,]$Lng <- convenience_store$geometry.location.lng[row.num]
  nearest_conve_store[1,]$Lat <- convenience_store$geometry.location.lat[row.num]
  
  return(list(nearest_conve_store, row.num))
}
```

```{r}
conv_store_df <- nearest_convenience_store(row.num1)
row.num2 <- nearest_convenience_store(row.num1)[[2]]
nearest_convenience_store(row.num1)
```


# get nearest shopping mall from convenience store
```{r}
library(geosphere)
library(dplyr)
shopping_mall <- shopping_mall[!is.na(shopping_mall$geometry.location.lng) & !is.na(shopping_mall$geometry.location.lat),]

nearest_shopping_mall <- function(n){
  nearest_shopping_mall <- data.frame(Nearest=NA, Distance=NA, Lng=NA, Lat=NA)
  
  conve_store.coords <- convenience_store[n,] %>% select(geometry.location.lng, geometry.location.lat)
  shopping_mall.coords <- shopping_mall %>% select(geometry.location.lng, geometry.location.lat)
  #distances <- distm(conve_store.coords, shopping_mall.coords, fun=distGeo)[1,]
  distances <- distm(origin.coords, conve_store.coords, fun=distGeo)[1,]
  diff <- abs(distances - 500)
  row.num <- which.min(diff)
  #row.num <- which.min(distances)
  
  nearest_shopping_mall[1,]$Nearest <- shopping_mall$name[row.num]
  nearest_shopping_mall[1,]$Distance <- distances[row.num] %>% round(-1) %>% as.integer
  nearest_shopping_mall[1,]$Lng <- shopping_mall$geometry.location.lng[row.num]
  nearest_shopping_mall[1,]$Lat <- shopping_mall$geometry.location.lat[row.num]
  
  return(list(nearest_shopping_mall, row.num))
}
```

```{r}
nearest_shopping_mall(row.num2)
```



# try osrm 
```{r}
library(osrm)
locs <- data.frame(id = c("Origin", "FairPrice Xpress", "FairPrice Xpress", "The Grandstand"),
                   lon = c(103.799000, 103.8065, 103.8065, 103.7934),
                   lat = c(1.330022, 1.331706, 1.331706	, 1.338008)
                   )

# TRIP
# Calculate the shortest round trip between the park locations
trip <- osrmTrip(locs
        ,returnclass = "sf", overview = "full", osrm.server = getOption("osrm.server"), osrm.profile= "foot")

# Get the spatial lines dataframe 
trip_sp <- trip[[1]]$trip

# PLOT WITH LEAFLET
leaflet(data = trip_sp) %>% 
  setView(lng = 103.8125, lat = 1.360729, zoom = 13) %>%
  addTiles() %>% 
  addMarkers(lng = locs$lon, lat = locs$lat, popup = locs$id) %>%
  addPolylines()
```

# get leg summary
```{r}
leg_summary <- trip_sp %>%
  mutate(duration = round(duration, 1),
         distance = round(distance, 1))

leg_summary
```
# trip summary
```{r}
# duration in min, distance in km
trip_summary <- trip[[1]]$summary
trip_summary
```
# try osrmRoute. fail!!
```{r}
library(osrm)
library(sf)

pts <- structure(
 list(x = c(103.799000, 103.8065, 103.7935, 103.7991, 103.799000), 
      y = c(1.330022, 1.331706, 1.337730, 1.330933, 1.330022)), 
class = "data.frame", row.names = c(NA, -10L))
route5 <- osrmRoute(loc = pts, returnclass = "sf")
plot(st_geometry(route5), col = "red", lwd = 2)
points(pts, pch = 20, cex = 2)

```





# plot the map using mapsapi - fail!!!not circular route
```{r}
library(mapsapi)
library(xml2)
key='AIzaSyAFwIr0aBkkLxXzihnK_LPlh-Ph77FZy44'



doc <- mp_directions(
  origin = c(103.799000 , 1.330022),
  waypoints = c(c(103.8065, 1.331706), c(103.7991, 1.330933), c(103.7935, 1.337730)),
  destination = c(103.799000 , 1.330022),
  alternatives = FALSE,
  key = key,
  mode = "walking",
  quiet = TRUE
) 
#the output is a XML document with Google Maps Geocode API response - whatever that means

doc = as_xml_document(doc) #apparently we have to read it into an XML document - whatever that means
r <- mp_get_routes(doc) #mp_get_routes is a function to uhm..get the route

#distance <- mp_get_matrix(doc, value="distance_m")

library(leaflet)

leaflet() %>% addTiles() %>% addPolylines(data = r, opacity = 1, weight = 4) #can specify other things here tbh
```
# 
```{r}
nxt_loc <- function(dist, curr.long.lat, next.loc){
  next_loc <- read.csv(gsub(" ", "", paste(gsub(" ", "_", next.loc), ".csv")))

  curr.long.latm <- matrix(curr.long.lat, ncol = 2)
  print(matrix(as.numeric(curr.long.latm), ncol = 2))
  next_loc <- next_loc %>%
    mutate(Distance = distHaversine(matrix(as.numeric(curr.long.latm), ncol = 2),
                                    matrix(c(as.numeric(geometry.location.lng),
                                             as.numeric(geometry.location.lat)),
                                           ncol = 2
                                           )
                                    )
           )

  index <- which.min(abs(dist - next_loc$Distance))
  print(index)
  closest.coordinate <- c(next_loc[index, "name"],
                          next_loc[index, "geometry.location.lng"],
                          next_loc[index, "geometry.location.lat"])
  
  return (closest.coordinate)
}


nearest.loc.mat <- function(dist, origin, ...){
  locations <- list(...)
  print(locations)
  if (is.null(locations)){
    return(0) # placeholder for when no locations are supplied as input arguments; to be replaced with function to generate random route that fulfills other restraints
    
  } else {
    output <- list(origin)
    
    for (location in locations){
      next.long.lat <- nxt_loc(dist, origin[-1], location)
      output <- append(output, next.long.lat)
      origin <- next.long.lat
    }
  }

  output <- matrix(unlist(output), ncol = 3, byrow = T)
  colnames(output) <- c("id", "Longitude", "Latitude")
  output <- data.frame(output)
  output$Longitude <- as.numeric(output$Longitude)
  output$Latitude <- as.numeric(output$Latitude)
  
  return (output)
}

plot_route <- function(curr_loc, locations){
  trip <- osrmTrip(locations, returnclass = "sf", overview = "full", osrm.server = getOption("osrm.server"), osrm.profile= "foot")
  trip_sp <- trip[[1]]$trip
  leaflet(data = trip_sp) %>%
    addTiles() %>% 
    addMarkers(lng = locations$Longitude, lat = locations$Latitude, popup = locations$id) %>%
    addPolylines()
}

route_summary <- function(curr_loc, locations){
  trip <- osrmTrip(locations, returnclass = "sf", overview = "full", osrm.server = getOption("osrm.server"), osrm.profile= "foot")
  trip_sp <- trip[[1]]$trip
  leg_summary <- trip_sp %>%
    mutate(duration = round(duration, 1),
           distance = round(distance, 1))

return (leg_summary)
}

overall <- function(curr_loc, locations){
  trip <- osrmTrip(locations, returnclass = "sf", overview = "full", osrm.server = getOption("osrm.server"), osrm.profile= "foot")
  trip_summary <- trip[[1]]$summary
  
  return (trip_summary)
}

curr_location <- c("my origin!", 103.799000, 1.330022)
inter_locations <- nearest.loc.mat(1000, curr_location, "cafe", "convenience stores", "shopping mall")
inter_locations
summary(inter_locations)
plot_route(curr_location, inter_locations)
route_summary(curr_location, inter_locations)
overall(curr_location, inter_locations)

```

